A large scale study of the languages spoken (by bilinguals) on Mechanical Turk

### 2013-02-19 writeup/paper.tex

\section{Background and Related Work}
%\section{Background on Mechanical Turk and Related Work}
%\section{Mechanical Turk}
Amazon's Mechanical Turk (MTurk) is an online marketplace for work which gives employers and researchers access to a large, low-cost, workforce. MTurk provides a simple interface for accessing human skills, allowing employers to provide micro-payments in return for workers completing micro-tasks.  The basic units of work on MTurk are called ``Human Intelligence Tasks'' (HITs),which hints at its origins.  MTurk was designed to accommodate tasks that are difficult for computers, but simple for people. This facilitates research into human computation, where people can be treated as a function call \cite{vonAhn2008,Little2009,quinn-bederson:2011}.  It has application to research areas like human-computer interaction \cite{bigham-et-al:2010,bernstein-et-al:2010}, computer vision  \cite{sorkin-forsyth:2008,deng-et-al:2010,rashtchian:10}, speech processing \cite{marge-banerjee-rudnicky:2010:MTURK,lane-EtAl:2010:MTURK,Parent-Eskenazi:2011,Eskenazi:2013:crowdsourcing-speech-book},  and natural language processing \cite{Snow2008,callisonburch-dredze:2010:MTURK,laws-scheible-schutze:2011:EMNLP}.

>>>>

\section{Background and Related Work}
%\section{Background on Mechanical Turk and Related Work}
%\section{Mechanical Turk}
Amazon's Mechanical Turk (MTurk) is an online marketplace for work that gives employers and researchers access to a large, low-cost, workforce. MTurk provides a simple interface for accessing human skills, allowing employers to provide micro-payments in return for workers completing micro-tasks.  The basic units of work on MTurk are called ``Human Intelligence Tasks'' (HITs),which hints at its origins.  MTurk was designed to accommodate tasks that are difficult for computers, but simple for people. This facilitates research into human computation, where people can be treated as a function call \cite{vonAhn2008,Little2009,quinn-bederson:2011}.  It has application to research areas like human-computer interaction \cite{bigham-et-al:2010,bernstein-et-al:2010}, computer vision  \cite{sorkin-forsyth:2008,deng-et-al:2010,rashtchian:10}, speech processing \cite{marge:10,lane-EtAl:2010:MTURK,Parent-Eskenazi:2011,Eskenazi:2013:crowdsourcing-speech-book},  and natural language processing \cite{Snow2008,callisonburch-dredze:2010:MTURK,laws-scheible-schutze:2011:EMNLP}.
